Fig 2

### 2020-08-21 analysis/figure-2-new.Rmd
better labels

b <- makebargraphv3(DEGcontrol, "hypothalamus","No. of DEGs\n (-) decreased, incrased (+)", comparisonlabelscontrol) +
  labs(title = "Control versus all other reproductive and parental stages",
       subtitle = "hypothalamus") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "B", size = 2.5)

c <- makebargraphv3(DEGbldg, "hypothalamus", "No. of DEGs\n (-) decreased, incrased (+)", comparisonlabelsbldg) +
  labs(title = "Nest-building versus all other parental stages",
       subtitle = "hypothalamus")
d <- makebargraphv3(DEGchar, "hypothalamus", NULL,  comparisonlabelscharnobldg) +
  labs(title = "Comparison of sequential parental stages",
       subtitle = "hypothalamus")

e <- makebargraphv3(DEGbldg, "pituitary", "No. of DEGs\n (-) decreased, incrased (+)", comparisonlabelsbldg) +
  labs(subtitle = "pituitary")
f <- makebargraphv3(DEGchar, "pituitary", NULL,comparisonlabelscharnobldg) +
  labs(subtitle = "pituitary")

g <- makebargraphv3(DEGbldg, "gonad", "No. of DEGs\n (-) decreased, incrased (+)", comparisonlabelsbldg) +
  labs(subtitle = "gonads")
h <- makebargraphv3(DEGchar, "gonad", NULL, comparisonlabelscharnobldg) +
  labs(subtitle = "gonads")

>>>>

b <- makebargraphv3(DEGcontrol, "hypothalamus","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(title = "Control versus all other reproductive and parental stages",
       subtitle = "hypothalamus") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "B", size = 2.5)

c <- makebargraphv3(DEGbldg, "hypothalamus", "No. of DEGs\n (-)decreased  increased (+)", comparisonlabelsbldg) +
  labs(title = "Nest-building versus all other parental stages",
       subtitle = "hypothalamus")
d <- makebargraphv3(DEGchar, "hypothalamus", NULL,  comparisonlabelscharnobldg) +
  labs(title = "Comparison of sequential parental stages",
       subtitle = "hypothalamus")

e <- makebargraphv3(DEGbldg, "pituitary", "No. of DEGs\n (-)decreased  increased (+)", comparisonlabelsbldg) +
  labs(subtitle = "pituitary")
f <- makebargraphv3(DEGchar, "pituitary", NULL,comparisonlabelscharnobldg) +
  labs(subtitle = "pituitary")

g <- makebargraphv3(DEGbldg, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlabelsbldg) +
  labs(subtitle = "gonads")
h <- makebargraphv3(DEGchar, "gonad", NULL, comparisonlabelscharnobldg) +
  labs(subtitle = "gonads")
